Framing Effects in the Wild: How the News Media Shapes Public Opinion by Defining Political Issues

### 2022-07-11 paper/Manuscript_Framing.Rmd
Add nulleffectplots

>>>>

```{r multidv, fig.cap="Standardised Effect of Change in Framing on Alternative Dependent Variables"}

EffectPlot(multi = T, scaled = T, boundary_share = 0.2) # 0.2 SD suggested by Peyton 2020, 599

```{r migwaves, fig.cap="Effect of Change in Framing on Immigration Attitudes across Waves"}

EffectByWavePlot(boundary_share = 1) 
# would add 2 (or 3) lines here: 
#   minimal relevant effect (5%/0.3 on 7-point scale); 
#   conservative experimental effect (10%/0.6)
#   large (not maximum) experimental effect (30%/2.4)
